Manuscript Figures

### 2018-06-06 Manuscript Figures.Rmd
Updated figures

```{r chromosome_plot, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=8, fig.height=4}
v4_subg_jw <-
  subgenome %>%
  left_join(positions, by=c("gene2"="geneID")) %>%
  select(Chromosome, Pos_start, Pos_end, subgenome) %>%
  rename(Subgenome=subgenome) %>%
  subset(Subgenome %in% c("sub1", "sub2"))

@@

df1 <- centromere.v4.positions
df1$x <- -.45
df1$xend <- .45
df2 <- v4_subg_jw
df2$x <- -.45
df2$xend <- -.05
df3 <- v4_dom_jw
df3$x <- .05
df3$xend <- .45
segment_data <- bind_rows(df2,df3)
segment_data <- segment_data[!is.na(segment_data$Pos_start),]
segment_data <-
  segment_data %>%
  ungroup()
segment_data <- segment_data %>% subset(Subgenome %in% c("sub1", "sub2", "orphan", "sub1dom", "sub2dom", "dom"))
centromere_data <- df1

#--------------------------------------------------------------------------------------------------#
## Make the plot
p <-
  ggplot(data=v4) +
    geom_bar(aes(v4$chromosome, v4$size), stat="identity", fill="grey70") +
    # geom_segment(data=segment_data, aes(x=Chromosome+x, xend=Chromosome+xend, y=Pos_start, yend=Pos_end, colour=Subgenome), size=.001) +
    geom_rect(data=segment_data, inherit.aes = F, aes(xmin=Chromosome+x, xmax=Chromosome+xend, ymin=Pos_start, ymax=Pos_end, color=Subgenome, fill=Subgenome)) +
    geom_rect(data=centromere_data, inherit.aes = F, aes(xmin=Chromosome+x, xmax=Chromosome+xend, ymin=Pos_start, ymax=Pos_end)) +
    scale_fill_manual(values=c("green", "red", "blue", "black")) +
    scale_color_manual(values=c("green", "red", "blue", "black")) +
    scale_x_discrete(limits=c("Chr1","Chr2","Chr3","Chr4","Chr5","Chr6","Chr7","Chr8","Chr9","Chr10")) +
    scale_y_continuous(labels=format_si())
p  +
  labs(
  # title="Subgenome Locations by Chromosome",
  x="Chromosome",
  y="Position on Chromosome"
)

@@

# 2 GO Term Comparison by Subgenome
***

GO Terms by subgenome.  If the GO Term is assigned to any gene in the subgenome, it is counted once for that subgenome.  This is a presence/absence test.

The main takeaways here are that 1) there are differences in functional assignments between each subgenome, regardless of which filters I apply.  2) the GOSlim for plants is extremely restrictive, and probably not useful.  3) Sub1 has more functional assignments than sub2, although this may be a direct correlation to the larger size (by definition) of sub1.

GO Term assignments to genes by subgenome, which takes into account the gene-GO Term pairings and considers homeologs equivalent for the purposes of determining overlap in assignments.

The main takeaways here mirror the assessment from the GO Term presence/absence check above. There are many differences in assignments, although we can assume that the same terms are reused very often based on the differenced between unique terms and gene annotations.

```{r GOTerms_by_subgenome, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=4, fig.height=4}
#EXP only, MF terms only
grid.newpage()
g <- draw.pairwise.venn(
  area1 = goAnnotations.sub1 %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% select(goTerm) %>% distinct() %>% nrow(),
  area2 = goAnnotations.sub2 %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% select(goTerm) %>% distinct() %>% nrow(),
  cross.area = intersect(goAnnotations.sub1 %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% select(goTerm) %>% distinct(),  
                         goAnnotations.sub2 %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% select(goTerm) %>% distinct()
                         ) %>% nrow(), 
  category = c("Maize1", "Maize2"), 
  lty = rep("blank", 2), 
  fill = c("light blue", "green"), 
  alpha = rep(0.5, 2), 
  cat.pos = c(0, 180), 
  scaled = FALSE,
  euler.d = FALSE, 
  sep.dist = 0.3, 
  rotation.degree = 0,
  ind = FALSE
)
grid.arrange(gTree(children=g), top="GO Term by Subgenome\n(EV-EXP, MF only)")

@@

#EXP only, MF only
grid.newpage()
g <- draw.pairwise.venn(
  area1 = goAnnotations.sub1 %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% nrow(),
  area2 = converted %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% nrow(),
  cross.area = intersect(goAnnotations.sub1 %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% select(gene2, goTerm) %>% distinct(), 
                         converted %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% select(gene2, goTerm) %>% distinct()
                         ) %>% nrow(), 
  category = c("Maize1", "Maize2"), 
  lty = rep("blank", 2), 
  fill = c("light blue", "green"), 
  alpha = rep(0.5, 2), 
  cat.pos = c(0, 180), 
  scaled = FALSE,
  euler.d = FALSE, 
  sep.dist = 0.3, 
  rotation.degree = 0,
  ind = FALSE
)
grid.arrange(gTree(children=g), top="GO Term Assignments by Subgenome\n(EV-EXP, MF only)")
```

# 3 Compare Homeolog Pairs

@@

```{r subgenome_isoforms_scatter, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.align='center', fig.cap = cap}
# Isoforms
data <-
  homeologs.pairs %>%
  subset(Maize1 != "" & Maize2 != "") %>%
  select(Maize1, Maize2) %>%
  distinct() %>%
  inner_join(geneTranscript.counts, by=c("Maize1"="gene")) %>%
  inner_join(geneTranscript.counts, by=c("Maize2"="gene"))
names(data)[3] <- "Value_maize1"
names(data)[4] <- "Value_maize2"
# data <- subset(data, data$Value_maize1 > 1 & data$Value_maize2 > 1) ## Ignore single-exon genes
data$foldChange <- log2(data$Value_maize1) - log2(data$Value_maize2)

@@

plot <-
  ggplot(subset(data, Value_maize1 <= 25 & Value_maize2 <= 25), aes(x=Value_maize1, y=Value_maize2)) +
  geom_point(position = "jitter", alpha=.1, aes(color = abs(foldChange))) +
  scale_color_gradient(low = "blue", high = "red") +
  geom_smooth(method="lm", se=TRUE, fullrange=FALSE, level=0.95) +
  geom_abline(mapping = null, data = null, slope = 1, intercept = 0) +
  # xlim(0,100) +
  # ylim(0,100) +
  xlim(0,25) +
  ylim(0,25) +
  labs(
    # title = paste0("Scatterplot of isoform counts for gene pair(s).\nExcludes ",n," outlier, alpha=.1, foldchange in log2, blue=lm fit."),
    x = "Isoform Counts for Maize1 Gene",
    y = "Isoform Counts for Maize2 Gene"
  ) + 
  # annotate("text",x=85,y=20, label=paste("Pearson Cor = ", round(cor(data$Value_maize1, data$Value_maize2, method = c("pearson")),2)))
  annotate("text",x=20,y=3, label=paste("Pearson Cor = ", round(cor(data$Value_maize1, data$Value_maize2, method = c("pearson")),2)))
plot(plot)

cap <- "Fig 3.1: "
```

```{r subgenome_expression_scatter_rep, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=8, fig.height=4, fig.align='center', fig.cap = cap}
maize.walley.v4mapped.expression.data <- 
  maize.walley.v4mapped.expression %>%
  select(geneID, sample, FPKM_avg)
data <-
  homeologs.pairs %>%
  subset(Maize1 != "" & Maize2 != "") %>%
  select(Maize1, Maize2) %>%
  distinct() %>%
  inner_join(maize.walley.v4mapped.expression.data, by=c("Maize1"="geneID")) %>%
  inner_join(maize.walley.v4mapped.expression.data, by=c("Maize2"="geneID", "sample"="sample")) %>%
  subset(!is.na(FPKM_avg.x) & !is.na(FPKM_avg.y))
names(data)[4] <- "Value_maize1"
names(data)[5] <- "Value_maize2"
# data <- subset(data, sample %in% c("Silk", "Embryo 20 DAP", "Leaf Zone 2 (Stomatal)"))

data <- 
  data %>%
  subset(sample %in% c("Primary Root 5 Days", "Mature Leaf 8", "6-7 internode"))

plot <-
  ggplot(data, aes(x=Value_maize1, y=Value_maize2)) +
  geom_point(alpha=.1, aes(color = sample)) +
  geom_abline(mapping = null, data = null, slope = 1, intercept = 0) +
  geom_smooth(method="lm", se=TRUE, fullrange=FALSE, level=0.95) +
  scale_x_log10() + scale_y_log10() +
  labs(
    # title = paste0("Scatterplot of expression for gene pair(s).\nAlpha=.1, reference line"),
    x = "Expression for Maize1 Gene (log scale)",
    y = "Expression for Maize2 Gene (log scale)"
  ) +
  theme(legend.position = "none") + facet_wrap(~sample, nrow=1)
plot(plot)

cap <- "Fig 3.2: "
```

```{r subgenome_expression_scatter, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=8, fig.height=8, fig.align='center', fig.cap = cap}
maize.walley.v4mapped.expression.data <- 
  maize.walley.v4mapped.expression %>%
  select(geneID, sample, FPKM_avg)
data <-
  homeologs.pairs %>%
  subset(Maize1 != "" & Maize2 != "") %>%
  select(Maize1, Maize2) %>%
  distinct() %>%
  inner_join(maize.walley.v4mapped.expression.data, by=c("Maize1"="geneID")) %>%
  inner_join(maize.walley.v4mapped.expression.data, by=c("Maize2"="geneID", "sample"="sample")) %>%
  subset(!is.na(FPKM_avg.x) & !is.na(FPKM_avg.y))
names(data)[4] <- "Value_maize1"
names(data)[5] <- "Value_maize2"
# data <- subset(data, sample %in% c("Silk", "Embryo 20 DAP", "Leaf Zone 2 (Stomatal)"))

plot <-
  ggplot(data, aes(x=Value_maize1, y=Value_maize2)) +
  geom_point(alpha=.1, aes(color = sample)) +
  geom_abline(mapping = null, data = null, slope = 1, intercept = 0) +
  geom_smooth(method="lm", se=TRUE, fullrange=FALSE, level=0.95) +
  scale_x_log10() + scale_y_log10() +
  labs(
    # title = paste0("Scatterplot of expression for gene pair(s).\nAlpha=.1, reference line"),
    x = "Expression for Maize1 Gene (log scale)",
    y = "Expression for Maize2 Gene (log scale)"
  ) +
  theme(legend.position = "none") + facet_wrap(~sample, nrow=6)
plot(plot)

cap <- "Fig 3.3: "
```

```{r subgenome_protein_scatter_rep, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=8, fig.height=4, fig.align='center', fig.cap = cap}
data <-
  homeologs.pairs %>%
  subset(Maize1 != "" & Maize2 != "") %>%
  select(Maize1, Maize2) %>%
  distinct() %>%
  inner_join(maize.walley.abundance.v4, by=c("Maize1"="geneID")) %>%
  inner_join(maize.walley.abundance.v4, by=c("Maize2"="geneID", "sample"="sample")) %>%
  subset(!is.na(dNSAF_avg.x) & !is.na(dNSAF_avg.y))
names(data)[4] <- "Value_maize1"
names(data)[5] <- "Value_maize2"
# data <- subset(data, sample %in% c("Silk", "Embryo 20 DAP", "Leaf Zone 2 (Stomatal)"))
data <- 
  data %>%
  subset(sample %in% c("Primary Root 5 Days", "Mature Leaf 8", "6-7 internode"))

plot <-
  ggplot(data, aes(x=Value_maize1, y=Value_maize2)) +
  geom_point(alpha=.1, aes(color = sample)) +
  geom_abline(mapping = null, data = null, slope = 1, intercept = 0) +
  geom_smooth(method="lm", se=TRUE, fullrange=FALSE, level=0.95) +
  scale_x_log10() + scale_y_log10() +
  labs(
    # title = paste0("Scatterplot of protein abundance for gene pair(s).\nAlpha=.1, reference line"),
    x = "Abundance for Maize1 Gene (log scale)",
    y = "Abundance for Maize2 Gene (log scale)"
  ) +
  theme(legend.position = "none") + facet_wrap(~sample, nrow=1)
  # + annotate("text", size=2, x=10000,y=10, label=paste("pearson: ", round(cor(data$Value_maize1, data$Value_maize2, method = c("pearson")),2)))
plot(plot)

cap <- "Fig 3.4: "
```

```{r subgenome_protein_scatter, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=8, fig.height=8, fig.align='center', fig.cap = cap}
data <-
  homeologs.pairs %>%
  subset(Maize1 != "" & Maize2 != "") %>%
  select(Maize1, Maize2) %>%
  distinct() %>%
  inner_join(maize.walley.abundance.v4, by=c("Maize1"="geneID")) %>%
  inner_join(maize.walley.abundance.v4, by=c("Maize2"="geneID", "sample"="sample")) %>%
  subset(!is.na(dNSAF_avg.x) & !is.na(dNSAF_avg.y))
names(data)[4] <- "Value_maize1"
names(data)[5] <- "Value_maize2"
# data <- subset(data, sample %in% c("Silk", "Embryo 20 DAP", "Leaf Zone 2 (Stomatal)"))

plot <-
  ggplot(data, aes(x=Value_maize1, y=Value_maize2)) +
  geom_point(alpha=.1, aes(color = sample)) +
  geom_abline(mapping = null, data = null, slope = 1, intercept = 0) +
  geom_smooth(method="lm", se=TRUE, fullrange=FALSE, level=0.95) +
  scale_x_log10() + scale_y_log10() +
  labs(
    # title = paste0("Scatterplot of protein abundance for gene pair(s).\nAlpha=.1, reference line"),
    x = "Abundance for Maize1 Gene (log scale)",
    y = "Abundance for Maize2 Gene (log scale)"
  ) +
  theme(legend.position = "none") + facet_wrap(~sample, nrow=6)
  # + annotate("text", size=2, x=10000,y=10, label=paste("pearson: ", round(cor(data$Value_maize1, data$Value_maize2, method = c("pearson")),2)))
plot(plot)

cap <- "Fig 3.5: "
```

# 4 Expression and Abundance are Weakly Correlated

```{r subgenome_expression_protein_foldchange_scatter, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=6, fig.height=5, fig.align='center', fig.cap = cap}
## Start with the paired expression data
maize.walley.v4mapped.expression.data <- 
  maize.walley.v4mapped.expression %>%
  select(geneID, sample, FPKM_avg)
data <-
  homeologs.pairs %>%
  subset(Maize1 != "" & Maize2 != "") %>%
  select(Maize1, Maize2) %>%
  distinct() %>%
  inner_join(maize.walley.v4mapped.expression.data, by=c("Maize1"="geneID")) %>%
  inner_join(maize.walley.v4mapped.expression.data, by=c("Maize2"="geneID", "sample"="sample")) %>%
  subset(!is.na(FPKM_avg.x) & !is.na(FPKM_avg.y))
names(data)[4] <- "FPKM_maize1"
names(data)[5] <- "FPKM_maize2"

@@

data$foldChange_expr <- log2(data$FPKM_maize1) - log2(data$FPKM_maize2)
data$foldChange_abun <- log2(data$dNSAF_maize1) - log2(data$dNSAF_maize2)
ggplot(data, aes(foldChange_expr, foldChange_abun)) +
  geom_point(alpha=.1) +
  xlim(-10,10) + ylim(-10,10) +
  geom_abline(mapping = null, data = null, slope = 1, intercept = 0) +
  geom_smooth(method="lm", se=TRUE, fullrange=FALSE, level=0.95) +
  # facet_wrap(~sample, nrow=6) +
  labs(
    # title = paste0("Scatterplot of Foldchange in Expression in Maize1 vs.\nFoldchange in Abundance in Maize1\nAlpha=.1, linear fit, n=13413"),
    x = "log2(Expression Maize1) - log2(Expression Maize2)",
    y = "log2(Abundance Maize1) - log2(Abundance Maize2)"
  ) + 
  annotate("text",x=7,y=-8, label=paste("Pearson Cor = ", round(cor(data$foldChange_expr, data$foldChange_abun, method = c("pearson")),2)))

cap <- "Fig 10.1: Considering only homeologous pairs where both genes were measured for expression and protein abundance, we look at fold change from maize2 expression to maize1 expression vs. the fold change from maize2 abundance vs. maize2 abundance. A slightly positive trend indicates a mild positive correlation between an increase in expression and an increase in abundance."
```

```{r subgenome_expression_protein_scatter, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=8, fig.height=8, fig.align='center', fig.cap = cap}
## Start with the paired expression data
maize.walley.v4mapped.expression.data <- 
  maize.walley.v4mapped.expression %>%
  select(geneID, sample, FPKM_avg)
data <-
  homeologs.pairs %>%
  subset(Maize1 != "" & Maize2 != "") %>%
  select(Maize1, Maize2) %>%
  distinct() %>%
  inner_join(maize.walley.v4mapped.expression.data, by=c("Maize1"="geneID")) %>%
  inner_join(maize.walley.v4mapped.expression.data, by=c("Maize2"="geneID", "sample"="sample")) %>%
  subset(!is.na(FPKM_avg.x) & !is.na(FPKM_avg.y))
names(data)[4] <- "FPKM_maize1"
names(data)[5] <- "FPKM_maize2"

>>>>

```{r chromosome_plot, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=8, fig.height=6}
v4_subg_jw <-
  subgenome %>%
  left_join(positions, by=c("gene2"="geneID")) %>%
  select(Chromosome, Pos_start, Pos_end, subgenome) %>%
  rename(Subgenome=subgenome) %>%
  subset(Subgenome %in% c("sub1", "sub2"))

@@

df1 <- centromere.v4.positions
df1$x <- -.45
df1$xend <- .45
df2 <- v4_subg_jw
df2$x <- -.45
df2$xend <- -.05
df3 <- v4_dom_jw
df3$x <- .05
df3$xend <- .45
segment_data <- bind_rows(df2,df3)
segment_data <- segment_data[!is.na(segment_data$Pos_start),]
segment_data <-
  segment_data %>%
  ungroup()
segment_data$Subgenome[segment_data$Subgenome %in% c("sub1")] <- "Maize1"
segment_data$Subgenome[segment_data$Subgenome %in% c("sub2")] <- "Maize2"
# segment_data$Subgenome[segment_data$Subgenome %in% c("dom")] <- "Dominant Homeolog"
segment_data <- segment_data %>% subset(Subgenome %in% c("Maize1", "Maize2", "orphan", "sub1dom", "sub2dom", "dom"))
centromere_data <- df1

#--------------------------------------------------------------------------------------------------#
## Make the plot
chromosome_plot <-
  ggplot(data=v4) +
    geom_bar(aes(v4$chromosome, v4$size), stat="identity", fill="grey70") +
    # geom_segment(data=segment_data, aes(x=Chromosome+x, xend=Chromosome+xend, y=Pos_start, yend=Pos_end, colour=Subgenome), size=.001) +
    geom_rect(data=segment_data, inherit.aes = F, aes(xmin=Chromosome+x, xmax=Chromosome+xend, ymin=Pos_start, ymax=Pos_end, color=Subgenome, fill=Subgenome)) +
    geom_rect(data=centromere_data, inherit.aes = F, aes(xmin=Chromosome+x, xmax=Chromosome+xend, ymin=Pos_start, ymax=Pos_end)) +
    scale_fill_manual(values=c("green", "red", "blue", "black")) +
    scale_color_manual(values=c("green", "red", "blue", "black")) +
    scale_x_discrete(limits=c("Chr1","Chr2","Chr3","Chr4","Chr5","Chr6","Chr7","Chr8","Chr9","Chr10")) +
    scale_y_continuous(labels=format_si())
chromosome_plot  +
  labs(
  # title="Subgenome Locations by Chromosome",
  x="Chromosome",
  y="Position on Chromosome"
)

@@

# 2 GO Term Comparison by Subgenome

```{r GOTerms_by_subgenome, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=4, fig.height=4}
#EXP only, MF terms only
grid.newpage()
GOTerms_by_subgenome_a <- draw.pairwise.venn(
  area1 = goAnnotations.sub1 %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% select(goTerm) %>% distinct() %>% nrow(),
  area2 = goAnnotations.sub2 %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% select(goTerm) %>% distinct() %>% nrow(),
  cross.area = intersect(goAnnotations.sub1 %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% select(goTerm) %>% distinct(),  
                         goAnnotations.sub2 %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% select(goTerm) %>% distinct()
                         ) %>% nrow(), 
  category = c("Maize1", "Maize2"), 
  lty = rep("blank", 2), 
  fill = c("light blue", "green"), 
  alpha = rep(0.5, 2), 
  cat.pos = c(0, 180), 
  scaled = FALSE,
  euler.d = FALSE, 
  sep.dist = 0.3, 
  rotation.degree = 0,
  ind = FALSE
)
grid.arrange(gTree(children=GOTerms_by_subgenome_a), top="GO Term by Subgenome\n(EV-EXP, MF only)")

@@

#EXP only, MF only
grid.newpage()
GOTerms_by_subgenome_b <- draw.pairwise.venn(
  area1 = goAnnotations.sub1 %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% nrow(),
  area2 = converted %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% nrow(),
  cross.area = intersect(goAnnotations.sub1 %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% select(gene2, goTerm) %>% distinct(), 
                         converted %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% select(gene2, goTerm) %>% distinct()
                         ) %>% nrow(), 
  category = c("Maize1", "Maize2"), 
  lty = rep("blank", 2), 
  fill = c("light blue", "green"), 
  alpha = rep(0.5, 2), 
  cat.pos = c(0, 180), 
  scaled = FALSE,
  euler.d = FALSE, 
  sep.dist = 0.3, 
  rotation.degree = 0,
  ind = FALSE
)
grid.arrange(gTree(children=GOTerms_by_subgenome_b), top="GO Term Assignments by Subgenome\n(EV-EXP, MF only)")

# 3 Isoforms

@@

```{r subgenome_isoforms_scatter, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.align='center'}
# Isoforms
data <-
  homeologs.pairs %>%
  subset(Maize1 != "" & Maize2 != "") %>%
  select(Maize1, Maize2) %>%
  distinct() %>%
  inner_join(geneTranscript.counts, by=c("Maize1"="gene")) %>%
  inner_join(geneTranscript.counts, by=c("Maize2"="gene"))
names(data)[3] <- "Value_maize1"
names(data)[4] <- "Value_maize2"
# data <- subset(data, data$Value_maize1 > 1 & data$Value_maize2 > 1) ## Ignore single-exon genes
data$foldChange <- log2(data$Value_maize1) - log2(data$Value_maize2)

@@

subgenome_isoforms_scatter <-
  ggplot(subset(data, Value_maize1 <= 25 & Value_maize2 <= 25), aes(x=Value_maize1, y=Value_maize2)) +
  geom_point(position = "jitter", alpha=.1, aes(color = abs(foldChange))) +
  scale_color_gradient(low = "blue", high = "red") +
  geom_smooth(method="lm", se=TRUE, fullrange=FALSE, level=0.95) +
  geom_abline(mapping = null, data = null, slope = 1, intercept = 0) +
  # xlim(0,100) +
  # ylim(0,100) +
  xlim(0,25) +
  ylim(0,25) +
  labs(
    # title = paste0("Scatterplot of isoform counts for gene pair(s).\nExcludes ",n," outlier, alpha=.1, foldchange in log2, blue=lm fit."),
    x = "Isoform Counts for Maize1 Gene",
    y = "Isoform Counts for Maize2 Gene"
  ) + 
  # annotate("text",x=85,y=20, label=paste("Pearson Cor = ", round(cor(data$Value_maize1, data$Value_maize2, method = c("pearson")),2)))
  annotate("text",x=20,y=3, label=paste("Pearson Cor = ", round(cor(data$Value_maize1, data$Value_maize2, method = c("pearson")),2)))
plot(subgenome_isoforms_scatter)

# 4 Expression

```{r subgenome_expression_scatter_rep, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=8, fig.height=2.5, fig.align='center'}
maize.walley.v4mapped.expression.data <- 
  maize.walley.v4mapped.expression %>%
  select(geneID, sample, FPKM_avg)
data <-
  homeologs.pairs %>%
  subset(Maize1 != "" & Maize2 != "") %>%
  select(Maize1, Maize2) %>%
  distinct() %>%
  inner_join(maize.walley.v4mapped.expression.data, by=c("Maize1"="geneID")) %>%
  inner_join(maize.walley.v4mapped.expression.data, by=c("Maize2"="geneID", "sample"="sample")) %>%
  subset(!is.na(FPKM_avg.x) & !is.na(FPKM_avg.y))
names(data)[4] <- "Value_maize1"
names(data)[5] <- "Value_maize2"
# data <- subset(data, sample %in% c("Silk", "Embryo 20 DAP", "Leaf Zone 2 (Stomatal)"))

data <- 
  data %>%
  subset(sample %in% c("Primary Root 5 Days", "Mature Leaf 8", "6-7 internode", "B73 Mature Pollen"))

subgenome_expression_scatter_rep <-
  ggplot(data, aes(x=Value_maize1, y=Value_maize2)) +
  geom_point(alpha=.1, aes(color = sample)) +
  geom_abline(mapping = null, data = null, slope = 1, intercept = 0) +
  geom_smooth(method="lm", se=TRUE, fullrange=FALSE, level=0.95) +
  scale_x_log10() + scale_y_log10() +
  labs(
    # title = paste0("Scatterplot of expression for gene pair(s).\nAlpha=.1, reference line"),
    x = "Expression for Maize1 Gene (log scale)",
    y = "Expression for Maize2 Gene (log scale)"
  ) +
  theme(legend.position = "none") + facet_wrap(~sample, nrow=1)
plot(subgenome_expression_scatter_rep)

```{r subgenome_expression_scatter, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=8, fig.height=8, fig.align='center'}
maize.walley.v4mapped.expression.data <- 
  maize.walley.v4mapped.expression %>%
  select(geneID, sample, FPKM_avg)
data <-
  homeologs.pairs %>%
  subset(Maize1 != "" & Maize2 != "") %>%
  select(Maize1, Maize2) %>%
  distinct() %>%
  inner_join(maize.walley.v4mapped.expression.data, by=c("Maize1"="geneID")) %>%
  inner_join(maize.walley.v4mapped.expression.data, by=c("Maize2"="geneID", "sample"="sample")) %>%
  subset(!is.na(FPKM_avg.x) & !is.na(FPKM_avg.y))
names(data)[4] <- "Value_maize1"
names(data)[5] <- "Value_maize2"
# data <- subset(data, sample %in% c("Silk", "Embryo 20 DAP", "Leaf Zone 2 (Stomatal)"))

subgenome_expression_scatter <-
  ggplot(data, aes(x=Value_maize1, y=Value_maize2)) +
  geom_point(alpha=.1, aes(color = sample)) +
  geom_abline(mapping = null, data = null, slope = 1, intercept = 0) +
  geom_smooth(method="lm", se=TRUE, fullrange=FALSE, level=0.95) +
  scale_x_log10() + scale_y_log10() +
  labs(
    # title = paste0("Scatterplot of expression for gene pair(s).\nAlpha=.1, reference line"),
    x = "Expression for Maize1 Gene (log scale)",
    y = "Expression for Maize2 Gene (log scale)"
  ) +
  theme(legend.position = "none") + facet_wrap(~sample, nrow=6)
plot(subgenome_expression_scatter)
```

# 5 Protein Abundance

```{r subgenome_protein_scatter_rep, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=8, fig.height=2.5, fig.align='center'}
data <-
  homeologs.pairs %>%
  subset(Maize1 != "" & Maize2 != "") %>%
  select(Maize1, Maize2) %>%
  distinct() %>%
  inner_join(maize.walley.abundance.v4, by=c("Maize1"="geneID")) %>%
  inner_join(maize.walley.abundance.v4, by=c("Maize2"="geneID", "sample"="sample")) %>%
  subset(!is.na(dNSAF_avg.x) & !is.na(dNSAF_avg.y))
names(data)[4] <- "Value_maize1"
names(data)[5] <- "Value_maize2"
# data <- subset(data, sample %in% c("Silk", "Embryo 20 DAP", "Leaf Zone 2 (Stomatal)"))
data <- 
  data %>%
  subset(sample %in% c("Primary Root 5 Days", "Mature Leaf 8", "6-7 internode", "B73 Mature Pollen"))

subgenome_protein_scatter_rep <-
  ggplot(data, aes(x=Value_maize1, y=Value_maize2)) +
  geom_point(alpha=.1, aes(color = sample)) +
  geom_abline(mapping = null, data = null, slope = 1, intercept = 0) +
  geom_smooth(method="lm", se=TRUE, fullrange=FALSE, level=0.95) +
  scale_x_log10() + scale_y_log10() +
  labs(
    # title = paste0("Scatterplot of protein abundance for gene pair(s).\nAlpha=.1, reference line"),
    x = "Abundance for Maize1 Gene (log scale)",
    y = "Abundance for Maize2 Gene (log scale)"
  ) +
  theme(legend.position = "none") + facet_wrap(~sample, nrow=1)
  # + annotate("text", size=2, x=10000,y=10, label=paste("pearson: ", round(cor(data$Value_maize1, data$Value_maize2, method = c("pearson")),2)))
plot(subgenome_protein_scatter_rep)
```

```{r subgenome_protein_scatter, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=8, fig.height=8, fig.align='center'}
data <-
  homeologs.pairs %>%
  subset(Maize1 != "" & Maize2 != "") %>%
  select(Maize1, Maize2) %>%
  distinct() %>%
  inner_join(maize.walley.abundance.v4, by=c("Maize1"="geneID")) %>%
  inner_join(maize.walley.abundance.v4, by=c("Maize2"="geneID", "sample"="sample")) %>%
  subset(!is.na(dNSAF_avg.x) & !is.na(dNSAF_avg.y))
names(data)[4] <- "Value_maize1"
names(data)[5] <- "Value_maize2"
# data <- subset(data, sample %in% c("Silk", "Embryo 20 DAP", "Leaf Zone 2 (Stomatal)"))

subgenome_protein_scatter <-
  ggplot(data, aes(x=Value_maize1, y=Value_maize2)) +
  geom_point(alpha=.1, aes(color = sample)) +
  geom_abline(mapping = null, data = null, slope = 1, intercept = 0) +
  geom_smooth(method="lm", se=TRUE, fullrange=FALSE, level=0.95) +
  scale_x_log10() + scale_y_log10() +
  labs(
    # title = paste0("Scatterplot of protein abundance for gene pair(s).\nAlpha=.1, reference line"),
    x = "Abundance for Maize1 Gene (log scale)",
    y = "Abundance for Maize2 Gene (log scale)"
  ) +
  theme(legend.position = "none") + facet_wrap(~sample, nrow=6)
  # + annotate("text", size=2, x=10000,y=10, label=paste("pearson: ", round(cor(data$Value_maize1, data$Value_maize2, method = c("pearson")),2)))
plot(subgenome_protein_scatter)
```

# 6 Expression and Abundance are Weakly Correlated

```{r subgenome_expression_protein_foldchange_scatter, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=6, fig.height=5, fig.align='center'}
## Start with the paired expression data
maize.walley.v4mapped.expression.data <- 
  maize.walley.v4mapped.expression %>%
  select(geneID, sample, FPKM_avg)
data <-
  homeologs.pairs %>%
  subset(Maize1 != "" & Maize2 != "") %>%
  select(Maize1, Maize2) %>%
  distinct() %>%
  inner_join(maize.walley.v4mapped.expression.data, by=c("Maize1"="geneID")) %>%
  inner_join(maize.walley.v4mapped.expression.data, by=c("Maize2"="geneID", "sample"="sample")) %>%
  subset(!is.na(FPKM_avg.x) & !is.na(FPKM_avg.y))
names(data)[4] <- "FPKM_maize1"
names(data)[5] <- "FPKM_maize2"

@@

# Remove pollen
data <-
  data %>%
  subset(!sample %in% c("B73 Mature Pollen"))

data$foldChange_expr <- log2(data$FPKM_maize1) - log2(data$FPKM_maize2)
data$foldChange_abun <- log2(data$dNSAF_maize1) - log2(data$dNSAF_maize2)
subgenome_expression_protein_foldchange_scatter <- ggplot(data, aes(foldChange_expr, foldChange_abun)) +
  geom_point(alpha=.1) +
  xlim(-10,10) + ylim(-10,10) +
  geom_abline(mapping = null, data = null, slope = 1, intercept = 0) +
  geom_smooth(method="lm", se=TRUE, fullrange=FALSE, level=0.95) +
  # facet_wrap(~sample, nrow=6) +
  labs(
    # title = paste0("Scatterplot of Foldchange in Expression in Maize1 vs.\nFoldchange in Abundance in Maize1\nAlpha=.1, linear fit, n=13413"),
    x = "log2(Expression Maize1) - log2(Expression Maize2)",
    y = "log2(Abundance Maize1) - log2(Abundance Maize2)"
  ) + 
  annotate("text",x=7,y=-8, label=paste("Pearson Cor = ", round(cor(data$foldChange_expr, data$foldChange_abun, method = c("pearson")),2))) + 
  annotate("text",x=7,y=-10, label=paste("Spearman Cor = ", round(cor(data$foldChange_expr, data$foldChange_abun, method = c("spearman")),2)))
plot(subgenome_expression_protein_foldchange_scatter)
```

```{r subgenome_expression_protein_scatter_rep, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=8, fig.height=2.5, fig.align='center'}
## Start with the paired expression data
maize.walley.v4mapped.expression.data <- 
  maize.walley.v4mapped.expression %>%
  select(geneID, sample, FPKM_avg)
data <-
  homeologs.pairs %>%
  subset(Maize1 != "" & Maize2 != "") %>%
  select(Maize1, Maize2) %>%
  distinct() %>%
  inner_join(maize.walley.v4mapped.expression.data, by=c("Maize1"="geneID")) %>%
  inner_join(maize.walley.v4mapped.expression.data, by=c("Maize2"="geneID", "sample"="sample")) %>%
  subset(!is.na(FPKM_avg.x) & !is.na(FPKM_avg.y))
names(data)[4] <- "FPKM_maize1"
names(data)[5] <- "FPKM_maize2"
